---
title: "Fitting Surrogates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fitting_surrogates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval=FALSE}
# One-time setup
library(reticulate)
envname = "r-reticulate"
conda_create(
  envname = envname,
  packages = c("pandas", "python=3.8")
)
keras::install_keras("conda", tensorflow="2.3.1", envname=envname)
conda_install(
  envname = envname,
  packages = c("keras2onnx", "onnxruntime"),
  pip = TRUE
)
```

```{r setup}
reticulate::use_condaenv('mlr3keras', required = TRUE)
devtools::load_all()
```

Creating a **BenchmarkConfig**:

All benchmarks have an associated **BenchmarkConfig** that contains paths to relevant files and other configurations required.

In order to fit surrogates or to get the objective we first instantiate the **Config** object.

```{r}
workdir = paste0(path.expand("~"), "/LRZ Sync+Share/multifidelity_data/")
cfg = BenchmarkConfigNB301$new(workdir = workdir)
```

or alternatively use the sugar:

```{r}
cfg = cfgs('nb301', workdir = workdir)
```

and start fitting a surrogate:

```{r}
cfg$fit_surrogate()
```

We can adjust the NeuralNet architecture and fitting parameters by supplying a `model_config`.

```{r}
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config)
```

**NOTE** per default, models are not saved. We can enable this by supplying `overwrite = TRUE`.

The same holds for all other models:



## LCBench

```{r}
cfg = cfgs('lcbench', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config)
```

## SVM

```{r}
cfg = cfgs('rbv2_svm', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

Check the results
```{r}
  obj = cfg$get_objective()
  des = paradox::generate_design_random(cfg$param_set, 10)
  data = rbindlist(des$transpose(FALSE))[,names(obj$domain$params), with=FALSE]
  obj$eval_dt(data)
```


```{r}
save_task_ids(cfg)
```

## Ranger

```{r}
cfg = cfgs('rbv2_ranger', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

And we save the task_ids to a text file.

```{r}
save_task_ids(cfg)
```

and check whether this works

```{r}
  obj = cfg$get_objective()
  des = paradox::generate_design_random(cfg$param_set, 10)
  data = rbindlist(des$transpose(FALSE))[,names(obj$domain$params), with=FALSE]
  obj$eval_dt(data)
```


## GLMNET

```{r}
cfg = cfgs('rbv2_glmnet', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

```{r}
  obj = cfg$get_objective()
  des = paradox::generate_design_random(cfg$param_set, 10)
  data = rbindlist(des$transpose(FALSE))[,names(obj$domain$params), with=FALSE]
  obj$eval_dt(data)
```

```{r}
save_task_ids(cfg)
```

## RPART

```{r}
cfg = cfgs('rbv2_rpart', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

```{r}
  obj = cfg$get_objective()
  des = paradox::generate_design_random(cfg$param_set, 10)
  data = rbindlist(des$transpose(FALSE))[,names(obj$domain$params), with=FALSE]
  obj$eval_dt(data)
```

```{r}
save_task_ids(cfg)
```

## XGBOOST

```{r, eval = FALSE}
cfg = cfgs('rbv2_xgboost', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

```{r}
  obj = cfg$get_objective()
  des = paradox::generate_design_random(cfg$param_set, 10)
  data = rbindlist(des$transpose(FALSE))[,names(obj$domain$params), with=FALSE]
  obj$eval_dt(data)
```

```{r}
save_task_ids(cfg)
```

## Aproximate KNN (aknn)

```{r, eval = FALSE}
cfg = cfgs('rbv2_aknn', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

```{r}
  obj = cfg$get_objective()
  des = paradox::generate_design_random(cfg$param_set, 10)
  data = rbindlist(des$transpose(FALSE))[,names(obj$domain$params), with=FALSE]
  obj$eval_dt(data)
```

```{r}
save_task_ids(cfg)
```


## SUPERLEARN

```{r, eval = FALSE}
cfg = cfgs('rbv2_super', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```

## FCNet

```{r}
cfg = cfgs('fcnet', workdir = workdir)
model_config = default_model_config()
model_config$epochs = 1L
model_config$activation = "relu"
cfg$fit_surrogate(model_config = model_config, overwrite = TRUE)
```


## Determining task_ids for evaluation

70 / 30 train-test split

```{r}
set.seed(444L)
keys = cfgs()$keys()
instances = rbindlist(map(keys, function(x) {
  cf = cfgs(x, workdir=workdir)

  test = TRUE
  if (startsWith("rbv2", x)) {
    test = cf$task_levels %in% rbv2_test_tasks
  }
  data.table(
    cfg = x,
    level = cf$task_levels,
    test = test
  )
}), fill=TRUE)
instances[sample(.N, ceiling(0.15 * .N)), test := FALSE, by = cfg]
instances[cfg == "fcnet", test := TRUE]
saveRDS(instances, "inst/instances.rds")
```

using it to obtain a list of `ObjectiveFunctions`.

```{r}
# The instantiation should probably not happen all together but later on.
instances = readRDS(system.file("instances.rds", package = "mfsurrogates"))
train = instances[test == FALSE, ]

# For each row, we can now instantiate the objective:
i = 1
cf = cfgs(train$cfg[i], workdir=workdir)
obj = cf$get_objective(train$level[i])
```